---
title: "Untitled"
author: "Devika Nair"
date: "5/29/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse) #includes ggplot2
```

## Data Formats

Difference between tibble & dataframe. Data frames are rectangular datasets.
Tibbles are data frames, but tweak some older behaviours to make life a littler easier.

Doubles - decimal value 
Integer - whole numbers
These designations exist because of the difference in memory required. 

If you hit tab inside the function's parantheses - it shows you the arguments. 

```{r cars}
mpg
head(mpg)
ggplot(data = mpg)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class))

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, size = class))

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, alpha = class)) # alpha - assigns shades of black

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, shape = class), color = 'blue')

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = 'blue') +
  facet_wrap(~class, nrow = 4)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = 'blue') +
  facet_grid(drv ~ cyl)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = 'blue') +
  geom_smooth(mapping = aes(x = displ, y = hwy)) 

```



```{r}
table(diamonds$cut)
library(tibble)
my_counts <- as_tibble(table(diamonds$cut))

france <- map_data('france')

ggplot(france, aes(long, lat, group = group)) +
  geom_polygon(fill = 'white', color = 'black') +
  coord_quickmap()

library(readr)

write_csv(x = diamonds, path = './') # defaults to something, hit tab to find out where
my_diamonds <- read_csv("~/diamonds.csv")


```








